Abstractions for Multi-Sorted Substitutions

### 2024-03-11 paper/paper.tex
Update.

  Building on the operations and axioms of a \ACode{\ACon{Kit}}, we
  define the usual operations for renamings and substitutions:\footnote{
    The definitions are included directly in the record module of the
    Kit, so they are implicitly parameterized over a kit.
  }
  \begin{itemize}
  \item 
    We unify the definition of renamings \ACode{S₁ \ADef{→ᵣ} S₂} and
    substitutions \ACode{S₁ \ADef{→ₛ} S₂}, which differ only in whether they
    return variables or terms:
    \LibCode\KMap
    We call a value of type \ACode{S₁ \ADef{→ₖ} S₂} a \emph{map} and
    use the meta-variable \ACode{ϕ} for it.
  \item 
    A map can be applied to a variable:
    \LibCode\KAp
  \item 
    A map can be extended by a new variable or term:
    \LibCode\KExt
  \item 
    A map can be shifted, as the \ACode{\ACon{Kit}} provides the
    necessary \ACode{\AField{wk}} operation:
    \LibCode\KWkm
  \item 
    A map can be lifted, which allows to
    move a map under a binder of sort \ACode{s}:
    \LibCode\KLift
  \item 
    There is an identity map:
    \LibCode\KId
  \item 
    There is a singleton map, which replaces \ACode{\ACon{zero}} and decreases
    all other variables by one:
    \LibCode\KSingle
  \item 
    There is a map which is equivalent to \ACode{\AField{wk}} on terms:
    \LibCode\KWeaken
  \item
    Maps have an extensional equality:
    \LibCode\KEq
  \item
    For simplicity we postulate functional extensionality:\footnote{
      The actual implementation does \emph{not} use any postulates.
      % The workaround is explained in Appendix~\ref{sec:fun-ext}.
    }
    \LibCode\KFunExt
  \item
    Lifting the identity map is a (larger) identity map:
    \LibCode\KIdLift
    % \LibCode\KIdLiftProof
  \end{itemize}

  We also specify notation, which makes it less cumbersome
  to explicitly pass a particular \ACode{\ACon{Kit}} to those definitions:
  \begin{itemize}
  \item
     we write \ACode{(S \ADef{∋/⊢[} K \ADef{]} s)} for the \ACode{(S ∋/⊢ s)}
     of some specific \ACode{\ACon{Kit}} \ACode{K}; and
   \item
     we write \ACode{(S \ADef{–[} K \ADef{]→} s)} for the \ACode{(S \ADef{→ₖ} s)}
     of some specific \ACode{\ACon{Kit}} \ACode{K}.
  \end{itemize}

@@

    % To get the \ACode{\ADef{CKit}} between substitutions and
    % renamings, the argument \ACode{\ADef{Cᵣ}} is used.
    % The resulting \ACode{\ADef{CKit}} is then again used as an argument
    % for \ACode{\ADef{Cₛ}} to yield the \ACode{\ADef{CKit}}
    % between two substitutions. As shown below, Agda's instance
    % resolution is up for the task:
    \LibCode\KCKitInstancesConcrete

>>>>

  Building on the operations and axioms of a \ACode{\ACon{Kit}}, we
  define the usual operations for renamings and substitutions:\footnote{
    The definitions are included directly in the record module of the
    Kit, so they are implicitly parameterized over a kit.
  }
  \begin{itemize}
  \item 
    We unify the definition of renamings \ACode{S₁ \ADef{→ᵣ} S₂} and
    substitutions \ACode{S₁ \ADef{→ₛ} S₂}, which differ only in whether they
    return variables or terms:
    \LibCode\KMap
    We call a value of type \ACode{S₁ \ADef{→ₖ} S₂} a \emph{map} and
    use the meta-variable \ACode{ϕ} for it.
  \item 
    A map can be applied to a variable:
    \LibCode\KAp
  % \item 
  %   A map can be extended by a new variable or term:
  %   \LibCode\KExt
  % \item 
  %   A map can be shifted, as the \ACode{\ACon{Kit}} provides the
  %   necessary \ACode{\AField{wk}} operation:
  %   \LibCode\KWkm
  \item 
    A map can be lifted, which allows to
    move a map under a binder of sort \ACode{s}:
    % \LibCode\KLift
    \LibCode\KLiftAlt
  \item 
    There is a singleton map, which replaces \ACode{\ACon{zero}} and decreases
    all other variables by one:
    \LibCode\KSingleAlt
  \item 
    There is a map which is equivalent to \ACode{\AField{wk}} on terms:
    \LibCode\KWeakenAlt
  \item
    Maps have an extensional equality:
    \LibCode\KEq
  \item
    For simplicity we postulate functional extensionality:\footnote{
      The actual implementation does \emph{not} use any postulates.
      % The workaround is explained in Appendix~\ref{sec:fun-ext}.
    }
    \LibCode\KFunExt
  \item 
    There is an identity map:
    \LibCode\KId
  \item
    Lifting the identity map is a (larger) identity map:
    \LibCode\KIdLift
    % \LibCode\KIdLiftProof
  \end{itemize}
  We also specify notation 
  to explicitly pass a particular \ACode{\ACon{Kit}} to those definitions:
  % We also specify notation, which makes it less cumbersome
  % to explicitly pass a particular \ACode{\ACon{Kit}} to those definitions:
  \begin{itemize}
  \item
     we write \ACode{(S \ADef{∋/⊢[} K \ADef{]} s)} for the \ACode{(S ∋/⊢ s)}
     of some specific \ACode{\ACon{Kit}} \ACode{K}; and
   \item
     we write \ACode{(S \ADef{–[} K \ADef{]→} s)} for the \ACode{(S \ADef{→ₖ} s)}
     of some specific \ACode{\ACon{Kit}} \ACode{K}.
  \end{itemize}

@@

    % To get the \ACode{\ADef{CKit}} between substitutions and
    % renamings, the argument \ACode{\ADef{Cᵣ}} is used.
    % The resulting \ACode{\ADef{CKit}} is then again used as an argument
    % for \ACode{\ADef{Cₛ}} to yield the \ACode{\ADef{CKit}}
    % between two substitutions. As shown below, Agda's instance
    % resolution is up for the task:
    \begin{minipage}[t]{0.5\linewidth}
    \LibCode\KCKitInstancesConcreteI
    \end{minipage}
    \begin{minipage}[t]{0.5\linewidth}
    \LibCode\KCKitInstancesConcreteII
    \end{minipage}
